Technical Interview

### 2017-09-03 tex/paper/paper.tex
Update the paper start the metrics

%%% PAGE DIMENSIONS
% Set up the paper to be as close as possible to both A4 & letter:
\settrimmedsize{11in}{210mm}{*} % letter = 11in tall; a4 = 210mm wide
\setlength{\trimtop}{0pt}
\setlength{\trimedge}{\stockwidth}
\addtolength{\trimedge}{-\paperwidth}
\settypeblocksize{*}{\lxvchars}{1.618} % we want to the text block to have golden proportionals
\setulmargins{50pt}{*}{*} % 50pt upper margins
\setlrmargins{*}{*}{1.618} % golden ratio again for left/right margins
\setheaderspaces{*}{*}{1.618}
\checkandfixthelayout 
\usepackage{enumitem}
\setitemize{noitemsep,topsep=0pt,parsep=0pt,partopsep=0pt}
\usepackage{xcolor,listings}
\usepackage{textcomp}
\lstset{upquote=true}
\usepackage{graphicx}
\usepackage{hyperref}
\hypersetup{
  colorlinks=true,
  linkcolor=blue,
  urlcolor=blue
}

@@

\newlength\drop
\makeatletter
\newcommand*\titleM{\begingroup%
\setlength\drop{0.08\textheight}
\centering
\vspace*{\drop}
{\Huge\bfseries Technical Interview}\\[\baselineskip]
%{\scshape MAN-AHL}\\[\baselineskip]
\vfill
\includegraphics[width=0.6\textwidth]{img/logo.png}\par\vspace{1cm}
\vfill
{\Huge\scshape Fadil Mokhchane \\ 
\small \href{https://www.linkedin.com/in/fadil/}{LinkedIn} }\par
\vspace{1cm}
\includegraphics[width=0.3\textwidth]{img/harrington.jpg}\par
\vfill
\vspace*{2\drop}
{\scshape September 1, 2017}\par
{\scshape \small Version 1.0}\par
\endgroup}
\makeatother
%% END Memoir customization

@@

\section{The Problem}
\label{sec:problem}
We interpret the question as the following the mathematical problem. 
We define a $X$ as a discrete random variable. 
As input, we have a $k$ values, $x_i$, with their associated probabilities, $p_i$.

@@

\section{Solution Proposed}
\subsection{Overview}

@@

\section{Implementation}

We use Haskell as implementation language. It is a purely functional language.
It has a strong type system. It is all about types, they tell the story.
In this section, we inztroduce the key types used thoughout the application.

@@

\subsection{Testing Module}

\section{Automated Unit and Integration Testing}
We need to test each module independtly, i.e. unit testing, and all used 
together, i.e. integration testing.

@@

@@

\section{Qualitative Testing}

\section{Performance Testing}

\section{Possible Extension}
Here is a list of possible extension we could add.
\begin{description}
	\item [Analytics]
	Further abstract the PDF, CDF, InvCDF to handle all kind of keys.
	\item [Testing]
	We could run the tests on different environments to ensure the portability of 
	the code.
	\item [UI] 
	A nice extension would be to add a Graphic User Interface,
	using the library 
	\href{https://hackage.haskell.org/package/threepenny-gui}{threepenny-gui}
	to create a portable Web application.

@@

\chapter{Code} \label{apx:code}
We provide below the code.

@@

Here are the steps to install the App.
\begin{enumerate}
	\item Download Haskell via this \href{https://www.haskell.org/platform/}{link}.
	\item Install following the instructions given by the installer.
	\item Use cabal to download the require packages :
\begin{lstlisting}[
           language=SQL,
           showspaces=false,
           basicstyle=\ttfamily,
           numbers=left,
           numberstyle=\tiny,
           commentstyle=\color{gray}
        ]
	cabal install TBC
\end{lstlisting}
\end{enumerate}
\end{document}

>>>>

%%% PAGE DIMENSIONS
% Set up the paper to be as close as possible to both A4 & letter:
\settrimmedsize{11in}{210mm}{*} % letter = 11in tall; a4 = 210mm wide
\setlength{\trimtop}{0pt}
\setlength{\trimedge}{\stockwidth}
\addtolength{\trimedge}{-\paperwidth}
\settypeblocksize{*}{\lxvchars}{1.618} % we want to the text block to have golden proportionals
\setulmargins{50pt}{*}{*} % 50pt upper margins
\setlrmargins{*}{*}{1.618} % golden ratio again for left/right margins
\setheaderspaces{*}{*}{1.618}
\checkandfixthelayout 
\usepackage{enumitem}
\setitemize{noitemsep,topsep=0pt,parsep=0pt,partopsep=0pt}
\usepackage{xcolor,listings}
\usepackage{textcomp}
\lstset{upquote=true}
\usepackage{graphicx}
\usepackage{subcaption}
\usepackage{hyperref}
\hypersetup{
  colorlinks=true,
  linkcolor=blue,
  urlcolor=blue
}

@@

\newlength\drop
\makeatletter
\newcommand*\titleM{\begingroup%
\setlength\drop{0.08\textheight}
\centering
\vspace*{\drop}
{\Huge\bfseries Technical Interview}\\[\baselineskip]
%{\scshape MAN-AHL}\\[\baselineskip]
\vfill
\includegraphics[width=0.6\textwidth]{img/logo.png}\par\vspace{1cm}
\vfill
{\Huge\scshape Fadil Mokhchane \\ 
\small \href{https://www.linkedin.com/in/fadil/}{CV on LinkedIn} }\par
\vspace{1cm}
\includegraphics[width=0.3\textwidth]{img/harrington.jpg}\par
\vfill
\vspace*{2\drop}
{\scshape September 3, 2017}\par
{\scshape \small Version 1.0}\par
\endgroup}
\makeatother
%% END Memoir customization

@@

%-------------------------------------------------------------------------------
\section{The Problem}
\label{sec:problem}
We interpret the question as the following the mathematical problem. 
We define a $X$ as a discrete random variable. 
As input, we have a $k$ values, $x_i$, with their associated probabilities, $p_i$.

@@

%-------------------------------------------------------------------------------
\section{Solution Proposed}
\subsection{Overview}

@@

%-------------------------------------------------------------------------------
\section{Implementation}

We use Haskell as implementation language. It is a purely functional language.
It has a strong type system. It is all about types, they tell the story.
In this section, we introduce the key types used thoughout the application.

\subsection{General Notes}
We use efficient data structures as appropriate and we modelise the problem using
the whole power of Haskell. 
We use \emph{newtype} as much as possible as it allows design at a 
seemless cost.

Indeed, we use parametric and ad hoc polymorphism as needs be.
We modelise the exception handling using different techniques, depending on
the context, let it be \emph{Either a b}, \emph{Maybe a} or \emph{error}.

The aim was to keep the software as simple as possible while targetting a
good design and performance. 
The right balance is always difficult to achieve as unfortunately no 
software is ever perfect.

The code is documented while we believe that a simple and well organised
code needs less documentation. The complexities are presented in the key
area of the code. The code is presented in \autoref{apx:code}.

Any constructive feedback is most welcome.

@@

\subsection{Testing Module}
We modelise a \emph{TestSuite} as a list of \emph{Test}.
Each \emph{Test} can be of different type: QuickCheck type - 
using a pseudo random data, 
an IO type - an action that need to be run, e.g. performance tests, 
and a Pure kind of test, for pure computation action.

%-------------------------------------------------------------------------------
\section{Unit and Integration Testing}
We need to test each module independtly, i.e. unit testing, and all used 
together, i.e. integration testing.

@@

We felt that the number of pillars was meant to be small. It is unlikely
the software will be used with a million pillars.

@@

%-------------------------------------------------------------------------------
\section{Qualitative Analysis}
We realise that we maybe be beyond the scope of the initial
question, which was to implement a \emph{nextNum} function.
However how to test it efficiently ? It is a very hard question.

It is an important part of Software Engineering and 
Quantitative Development to understand the 
meaning of what we are trying to achieve. 
It allows better modelisation, algoritms and testing. 
In this section, we will look at the number generated and try
to find the best parameters for this software.

\subsection{Metrics}
To assess the quality of a random number engine, we use
simple statistics. It would have been nice to have time to 
study further statistical and mathematical papers related 
to the random numbers generation and probabilities.
We could have created with more advanced metrics.

There are two keys elements which drive the results :
the input discrete probability function with $k$ pillars and
the output discrete probability function deducted from a
simulation of $n$ random numbers.

Hence we look at different input PDF with various $k$,
and the output PDF with various $n$. 
This data gives us intuitions about what are the right
parameters, $n$ and $k$ to use for our engines.

We also have two random numbers generator, 
Mersenne and Ecuyer, available. We compare them thoughout.

As our weighted probability engine depends on
the uniform probability engine. 
We test first the uniform engine.

The metrics we look at are:
\begin{itemize}
	\item the difference between the input and output pdf,
	\item the standard deviation of these differences,
	\item the mean of these difference, hopefully close to zero.
\end{itemize}

\subsection{Uniform Distribution}

The input PDF for a uniform distribution is flat. The probabilities
should be the same for each bucket.

\begin{figure}[h!]
    \centering
    \begin{subfigure}[b]{0.45\textwidth}
        \includegraphics[width=\textwidth]{img/uni-m-1.png}
        \caption{A gull}
        \label{fig:gull}
    \end{subfigure}
    ~ %add desired spacing between images, e. g. ~, \quad, \qquad, \hfill etc. 
      %(or a blank line to force the subfigure onto a new line)
    \begin{subfigure}[b]{0.45\textwidth}
        \includegraphics[width=\textwidth]{img/uni-m-1.png}
        \caption{A tiger}
        \label{fig:tiger}
    \end{subfigure}

    \begin{subfigure}[b]{0.45\textwidth}
        \includegraphics[width=\textwidth]{img/uni-m-1.png}
        \caption{A gull}
        \label{fig:gull}
    \end{subfigure}
    ~ %add desired spacing between images, e. g. ~, \quad, \qquad, \hfill etc. 
      %(or a blank line to force the subfigure onto a new line)
    \begin{subfigure}[b]{0.45\textwidth}
        \includegraphics[width=\textwidth]{img/uni-m-1.png}
        \caption{A tiger}
        \label{fig:tiger}
    \end{subfigure}

    \begin{subfigure}[b]{0.45\textwidth}
        \includegraphics[width=\textwidth]{img/uni-m-1.png}
        \caption{A gull}
        \label{fig:gull}
    \end{subfigure}
    ~ %add desired spacing between images, e. g. ~, \quad, \qquad, \hfill etc. 
      %(or a blank line to force the subfigure onto a new line)
    \begin{subfigure}[b]{0.45\textwidth}
        \includegraphics[width=\textwidth]{img/uni-m-1.png}
        \caption{A tiger}
        \label{fig:tiger}
    \end{subfigure}
    \caption{Pictures of animals}\label{fig:animals}
\end{figure}

\subsection{Weighted Distribution}

%-------------------------------------------------------------------------------
\section{Performance Analysis}

\subsection{Complexity Analysis}

\subsection{Uniform Engine Performance}

\subsection{Weighted Engine Performance}

%-------------------------------------------------------------------------------
\section{Conclusion}

%-------------------------------------------------------------------------------
\section{Possible Extensions}
Here is a list of possible extension we could add.
\begin{description}
	\item [Analytics]
	Further abstract the PDF, CDF, InvCDF to handle all kind of keys.
	\item [Code Design]
	We wonder if there was a way to avoid the \emph{MultiParamTypeClasses}
	extension and to achieve a better design. 
	Unfortunately time didn't allow further explorations.
	\item [Testing]
	We could run the tests on different environments to ensure the portability of 
	the code.
	\item [UI] 
	A nice extension would be to add a Graphic User Interface,
	using the library 
	\href{https://hackage.haskell.org/package/threepenny-gui}{threepenny-gui}
	to create a portable Web application.

@@

\chapter{Code} \label{apx:code}
We provide below the code. It is screenshots from 
\href{https://vim.sourceforge.io/}{Vim} with the 
\href{https://github.com/begriffs/haskell-vim-now}{haskell-vim-now}.
extension.

@@

Here are the steps to install the App.
\begin{enumerate}
	\item Download Haskell via this \href{https://www.haskell.org/platform/}{link}.
	\item Install following the instructions given by the installer.
	\item Use cabal to download the require packages :
\begin{itemize}
	\item mersenne-random-pure64
	\item countainers
	\item random
	\item mtl
	\item QuickCheck
	\item deepseq
\end{itemize}
\end{enumerate}
\end{document}
